%%%
%
% $Autor: Sudeshna Nanda$
% $Datum: 2024-10-19 $
% $Version: 1 $
% $Pfad: ML23-06-Magic-Wand-with-an-Arduino-Nano-33-BLE-sense/manual/Contents/en/GetStarted.tex $
% !TeX spellcheck = de_DE/GB
%
%%%



\chapter{Getting Started}

\section{Getting Started}

\begin{enumerate}
	
	\item \textbf{Unbox Your Wand:} \\
	Open the packing and take out your Magic Wand carefully. It includes a quick start instruction and the Magic Wand itself.
	\item \textbf{Acquaint yourself with the Wand:}\\
	Take a moment to familiarize self with the feel and balance of your Magic Wand. Observe its elegant design, meticulously crafted to fit comfortably in your hand, enabling precise control over your magical gestures.
	\item \textbf{Harness the Power:}\\
	Connect the board with the power bank to check if the board initiate successfully
	\item \textbf{Follow the setup Guidelines:}\\
	Comply with the setup section and complete these steps at the PC
	\item \textbf{Rehearse Gestures:}\\
	Practice the basic gestures outlined in the manual. 
	
\end{enumerate}

\section{Ready to Cast}

All Set to Cast,
Your Magic Wand is now attuned to your movements and prepared to bring your spells to life after the initial setup is finished. Your magical experience will be enhanced as you get more acquainted with the wand's capabilities and realize the full potential of its gesture detection and light effects.


Recall that the Magic Wand is an imaginative and creative instrument. Investigate its characteristics, try out different movements, and uncover its charm. Let's enjoy!


