%%%%%%
%
% $Autor: Sudeshna Nanda $
% $Datum: 2024-10-21 $
% $Pfad: ML23-06-Magic-Wand-with-an-Arduino-Nano-33-BLE-sense/manual/Contents/en/Warranty.tex $
% $Version: 1 $
%
%%%%%%

\chapter{Warranty}

\subsection{International Guarantee}
If you purchased the device from an authorized Magic Wand dealer, you are entitled to a free repair of the unit within a year of your purchase. The Magic Wand dealer is in charge of all after-purchase services. Any problems arising from mishaps, abuse, overuse, regular wear and tear, negligence, or unapproved repairs and modifications release the manufacturer from all liability. Furthermore, any loss or damage that arises during the unit's transportation to or from the person filing the warranty claim is not the manufacturer's responsibility. The section on warranty conditions contains the specific terms of the guarantee. 

\subsection{The warranty extends to}
Parts (excluding disc drives) and labor costs for one year from the purchase date (see below for additional terms and conditions). After one years you must pay for both parts and labor costs.
Disc drives (of any type) are covered under this warranty for one year from the purchase date.
Battery replacement is not covered by the warranty at any point.
At no point does the warranty cover the cost of transportation.

\subsection{Assurance-backed claims}
Please return this item to the dealer where you purchased it, using the original packing. Rather than using the postal service, it is advised to mail it via a reputable courier service with prepaid carriage. When the equipment is being shipped to the dealer or distributor, we are not liable for it. It is therefore wise to obtain equipment insurance to guard against any possible loss or damage while in transit. For additional information, please reach out to Magic Wand at XXX@magic-wand.com
\subsection{Query}
If your dealer is unable to answer any query regarding this or any other Magic Wand related-product please contact our Customer Support at the above address and we will do our best to help you.
\subsection{Online Registration}
You can register your product on-line at www.magic-wand.com. Moreover, extra 6 months will provide to customers who register through online. 

\subsection{Warranty Conditions}
\begin{enumerate}
	\item When warranty servicing is needed, the warranty is only valid if the warranty card is correctly filled out, together with the original sales slip, invoice, or confirmation, and the product's serial number hasn't been tampered with.
	\item Our obligations are limited to the repair or, at its discretion, replacement of the product or the defective part.
	\item Only Qualified Service Centers or Authorized Magic Wand Dealers are permitted to perform warranty repairs. For repairs performed by unapproved dealers, there will be no reimbursement, and this guarantee will not cover any harm these repairs may cause to the items.
	\item The product in question does not meet national or local technical or safety standards that apply in any other country than the one for which it was developed and made, hence it is not deemed to be defective in terms of materials or workmanship.
	\item This warranty covers none of the following:
	\begin{itemize}
		\item Periodic check ups, maintenance and repair or replacement of parts due to normal wear and tear.
			\item Performance due to differences in broadcasting method between countries.
			\item Misuse, including the failure to use this product for its normal purposes or incorrect installation
		\item Cost relating to transport, removal or installation of the product.
		\item Damage caused by Lightning, Water, Fire, Acts of God, War, Public Disturbances, incorrect mains voltage, improper ventilation or any other cause beyond the control of our team.
		\item Spillage of food or liquid or use of any other hazardous substances, which may effect the product.
	
	\end{itemize}
	\item This warranty is valid for any person who legally acquired possession of the product during the warranty period.
	\item This warranty does not affect the consumer's statutory rights under any applicable national legislation, whether those rights are against the merchant stemming from the purchase contract or not. The only rights under this warranty belong to the customer, unless there is a national law that states otherwise. Samsung, its affiliates, and distributors will not be held responsible for any indirect or consequential loss or damage to audio tapes, videos, compact discs, records, or any other related equipment or material.
	\item Some products may differ from these guidelines. Please check with your dealer or the local website. 
\end{enumerate}