%%%
%
% $Autor: Chung Man Tsang $
% $Datum: 2023-10-15 $

%
% !TeX spellcheck = de_DE/GB
%
%%%


\chapter{Important Safety Instructions}

\begin{enumerate}	
	\item Please read the Safety Instructions before using your Magic Wand
	\item Keep these instructions
	\item Heed all warnings
	\item Follow all instructions
	\item Clean only with clean tower
	\item Do not charge near any heat sources such as radiators, heat registers, stoves or other apparatus (including amplifiers) that produce heat
	\item Only use attachments/accessories specified by the
	manufacturer.
	\item Object or liquid entry
	WARNING – Do not expose this apparatus to rain or place it near water (near a bathtub, washbowl, kitchen sink, or laundry
	tub, in a wet basement, or near a swimming pool, etc.). The equipment shall not be exposed to dripping or splashing. Liquid-filled objects such as vases should not be placed on the equipment, as this can result in a electric shock. 
	\item This apparatus uses batteries. In your community, there might be environmental regulations that require you to
	dispose of these batteries properly. Please contact your local authorities for disposal or recycling information
	\item To protect this apparatus from unused for long periods of time, disconnect all the batteries from the battery compartment. This will prevent damage to the set due to battery leakage. 
	\item Climate -- The equipment has been designed for use in
	moderate climates and in domestic situations
	\item Abnormal smell -- If an abnormal smell or smoke is detected from the equipment, unplug the equipment from the USB-Port. Contact your dealer and do not reconnect the equipment
	\item Damage requiring service 
	The equipment should be serviced by qualified service personnel when:
	A. The power-supply cord or the plug has been
	damaged, or
	B. Objects have fallen, or liquid has spilled into the
	equipment, or
	C. The equipment has been exposed to rain, or
	D. The equipment does not appear to operate
	normally or exhibits a marked change in
	performance, or
	E. The equipment has been dropped or the
	enclosure damaged.
\end{enumerate}