%%%%%%%%%%%%
%
% $Autor: Adhiraj $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: AddOns.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Add Ons}

\section{Project Folder Structure}

\begin{lstlisting}[
	basicstyle=\ttfamily\footnotesize, 
	frame=single, 
	numbers=none, 
	caption=Project Directory Structure, 
	captionpos=b, 
	label=lst:project_structure
	]
	Project Root
	|- src/
	|- main.cpp
	|- imu_processing.cpp
	|- ml_model.cpp
	|- gesture_recognition.cpp
	|- include/
	|- imu_processing.h
	|- ml_model.h
	|- gesture_recognition.h
	|- models/
	|- magic_gestures.tflite
	|- scripts/
	|- data_collection.py
	|- model_training.py 
\end{lstlisting}

Reference to the structure: See Listing~\ref{lst:project_structure}.


\section{File Descriptions}


\subsection*{\texttt{src/}}
Contains the main application code.

\begin{itemize}
	\item \texttt{main.cpp}: Serves as the entry point of the program, initializing and orchestrating the overall flow.
	\item \texttt{imu\_processing.cpp}: Handles data collection from IMU (Inertial Measurement Unit) sensors, including filtering or preprocessing data.
	\item \texttt{ml\_model.cpp}: Loads and interfaces with the pre-trained TensorFlow Lite model, running inference on the processed IMU data.
	\item \texttt{gesture\_recognition.cpp}: Contains the logic for recognizing specific gestures based on model predictions.
\end{itemize}

\subsection*{\texttt{include/}}
Header files for the source files, defining necessary interfaces and dependencies.

\begin{itemize}
	\item \texttt{imu\_processing.h}: Declares the functions and classes for IMU processing.
	\item \texttt{ml\_model.h}: Declares the model loading and inference functions.
	\item \texttt{gesture\_recognition.h}: Declares the gesture recognition logic functions.
\end{itemize}

\subsection*{\texttt{models/}}
Stores machine learning models.

\begin{itemize}
	\item \texttt{magic\_gestures.tflite}: The pre-trained TensorFlow Lite model used for gesture classification.
\end{itemize}

\subsection*{\texttt{scripts/}}
Python scripts for data collection and model training.

\begin{itemize}
	\item \texttt{data\_collection.py}: Used to collect motion data, typically in the form of raw IMU sensor readings.
	\item \texttt{model\_training.py}: Handles the training of the machine learning model, potentially generating \texttt{magic\_gestures.tflite}.
\end{itemize}




