%%%%%%%%%%%%
%
% $Autor: Adhiraj $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: Functions.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Functions}

\section{Assembly Functions}

\subsection{Microcontroller Integration}
\begin{itemize}
	\item Mount the Arduino Nano 33 BLE Sense inside the wand casing.
	\item Ensure the USB port remains accessible for firmware updates and charging.
\end{itemize}

\subsection{Firmware Installation}
\begin{itemize}
	\item Load the gesture recognition firmware onto the microcontroller.
	\item Install necessary libraries (TensorFlowLite, Arduino\_LSM9DS1, etc.).
\end{itemize}

\subsection{Sensor Configuration}
\begin{itemize}
	\item Utilize the onboard IMU (LSM9DS1) for motion detection.
	\item Calibrate the IMU to detect specific gestures accurately.
\end{itemize}

\subsection{External Component Assembly}
\begin{itemize}
	\item Install RGB LED for visual feedback.
	\item Set up the vibration motor for haptic feedback.
	\item Secure wiring inside the casing.
\end{itemize}

\subsection{Final Casing Assembly}
\begin{itemize}
	\item 3D-print or fabricate a custom wand enclosure.
	\item Assemble and seal the casing while keeping essential ports accessible.
\end{itemize}

\section{Manufacturing Functions}

\subsection{PCB and Component Sourcing}
\begin{itemize}
	\item Procure Arduino Nano 33 BLE Sense and other electronic components.
	\item Source RGB LEDs, vibration motors, and connectors from reliable suppliers.
\end{itemize}

\subsection{Casing Fabrication}
\begin{itemize}
	\item Use 3D printing or injection molding to create the wand shell.
	\item Choose durable and lightweight materials for the enclosure.
\end{itemize}

\subsection{Circuit Integration}
\begin{itemize}
	\item Design and assemble the wiring layout for components.
	\item Ensure proper soldering and insulation to prevent short circuits.
\end{itemize}

\subsection{Testing and Calibration}
\begin{itemize}
	\item Run diagnostics on the IMU sensor to verify gesture detection accuracy.
	\item Test LED and vibration feedback to confirm responsiveness.
\end{itemize}

\subsection{Quality Control and Packaging}
\begin{itemize}
	\item Conduct functional tests on each assembled unit.
	\item Package the wand with necessary documentation and accessories (USB cable, instructions).
\end{itemize}

