%%%%%%%%%%%%
%
% $Autor: Sudeshna $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: ListOfParts.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{List Of Parts}

\section{List of Parts}
\subsection{Assembled Parts}
Pre-manufactured components that are integrated into the wand:
\begin{itemize}
	\item Arduino Nano 33 BLE Sense – Microcontroller with built-in sensors for motion and gesture recognition.
	\item LiPo Battery / Battery Pack – Power source (3.7V LiPo or AAA with a boost converter).
	\item RGB LED / NeoPixel – For magical lighting effects at the tip of the wand.
	\item Vibration Motor (Optional) – Provides haptic feedback for spellcasting.
	\item Push Button (Optional) – Allows user interaction for specific spell triggers.
	\item Thin Copper Wires – Connects components within the wand.
	\item Resistors \& Voltage Regulator (if needed) – Ensures correct voltage supply to components.
\end{itemize}

\subsection{Manufactured Parts}
Custom-made or externally fabricated components:
\begin{itemize}
	\item Wand Casing – Made of wood, plastic, or 3D-printed material to house all components.
	\item Internal Mounts / Holders – 3D-printed or handcrafted supports for securing components inside the wand.
	\item Custom PCB (Optional) – If a compact circuit board is designed for better integration.
	\item Enclosure for Battery – A secure holder for battery placement within the wand.
\end{itemize}


\section{List of Items}

\begin{table}[h]
	\centering
	\begin{tabular}{|l|l|c|l|}
		\hline
		\textbf{Item} & \textbf{Description} & \textbf{Price} & \textbf{Source} \\
		\hline
		Arduino Nano 33 BLE Sense & Microcontroller with built-in IMU \& BLE & \$35 & Amazon \\
		USB Cable & Micro USB cable for power \& programming & \$5 & Amazon \\
		3D-Printed Case & Custom wand enclosure & \$10 & Custom \\
		RGB LED & Optional lighting effect & \$3 & Amazon \\
		Vibration Motor & Optional haptic feedback & \$4 & Amazon \\
		\hline
	\end{tabular}
	\caption{List of necessary components for assembly}
\end{table}
