%%%%%%%%%%%%
%
% $Autor: Srikanth $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: Maintenance.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Maintenance}

\section{Hardware Maintenance}
\subsection{Avoiding Physical Damage}
\begin{itemize}
	\item \textbf{Use a protective casing:} Shield the Arduino board and sensors from dust and physical impacts.
	\item \textbf{Secure all connections:} Ensure wires, sensors, and external modules are firmly connected to prevent loose wiring issues.
\end{itemize}

\subsection{Cleaning and Dust Protection}
\begin{itemize}
	\item \textbf{Compressed air:} Use compressed air to remove dust from the board and sensors.
	\item \textbf{Antistatic brush:} Gently brush dirt away from the PCB and sensor components.
	\item \textbf{Isopropyl alcohol (IPA 99\%):} Dampen a microfiber cloth with IPA and gently clean the PCB, avoiding direct contact with sensors.
\end{itemize}

\subsection{Power Management}
\begin{itemize}
	\item \textbf{Use a quality power source:} Avoid using cheap USB adapters to prevent voltage fluctuations.
	\item \textbf{Battery care:} If using a Li-Po battery, ensure it is not overcharged or discharged below 3.3V to prolong its lifespan.
\end{itemize}

\section{Sensor Calibration and Maintenance}
The Arduino Nano 33 BLE Sense includes various sensors such as the IMU, microphone, and temperature sensor. Periodically recalibrating the sensors ensures accurate readings.

\subsection{IMU (Inertial Measurement Unit) Calibration}
\begin{itemize}
	\item \textbf{Run the self-test:} Use the self-test function available in most IMU libraries.
	\item \textbf{Allow stabilization:} Keep the wand stationary for a few seconds after powering it on to allow the IMU to stabilize.
	\item \textbf{Manual offset calibration:} Log raw accelerometer and gyroscope values, and adjust offsets in the code.
\end{itemize}

\subsection{Temperature and Humidity Sensor Care}
\begin{itemize}
	\item \textbf{Avoid moisture exposure:} High humidity may affect sensor accuracy.
	\item \textbf{Reset the sensor:} Restart the board and reinitialize the sensor if readings drift.
\end{itemize}

\section{Software and Firmware Maintenance}
\begin{itemize}
	\item \textbf{Update firmware and libraries:} Ensure you are using the latest version of Arduino firmware and sensor libraries.
	\item \textbf{Run diagnostic tests:} Periodically check sensor outputs using diagnostic scripts.
	\item \textbf{Log and analyze data:} Store sensor logs to detect any unusual trends or malfunctioning over time.
\end{itemize}



