%%%%%%%%%%%%
%
% $Autor: Sudeshna $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: SafetyGuidelines.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Safety Guidelines}

\section*{Important Safety Instructions}

\begin{enumerate}[label=\textbf{\arabic*.}]
	\item Please read the Safety Instructions before using your Magic Wand.
	\item Heed all warnings.
	\item Clean only with hygienic towel.
	\item Use attachments and accessories only from reputable manufacturers.
	\item Avoid placing near any heat sources, including stoves, heat registers, radiators, and other appliances that emit heat, including amplifiers.
	\item \textbf{Object or liquid entry WARNING:} Avoid exposing the apparatus to rain or water, including near bathtubs, sinks, or pools. Do not place liquid-filled objects on it, as this may cause electric shock.
	\item This apparatus uses power banks. Check with local authorities for proper disposal or recycling guidelines, as there may be environmental regulations.
	\item Disconnect power banks when not in use, especially if children, elderly, or disabled individuals are present. This helps prevent damage from battery leakage.
	\item \textbf{Climate:} The gadget has been engineered for application in moderate climates and in domestic situations.
	\item \textbf{Abnormal smell or sound:} If any foul smell or sound is detected from the equipment, unplug the cable from the Micro-USB Port and Power banks. Contact your authorized dealer or service center and do not reconnect the equipment.
	\item \textbf{Damage requiring services:} The equipment should be serviced by qualified service personnel when:
	\begin{itemize}
		\item The power-supply or the cable has been damaged, or
		\item Objects have fallen, or liquid has spilled into the equipment, or
		\item The equipment has been exposed to rain, or
		\item The hardware does not appear to operate normally or exhibits a marked change in performance, or
		\item The equipment has been dropped or the enclosure damaged.
	\end{itemize}
	\item The figures and illustrations in this User Manual may not exactly match the appearance of the product; they are only meant to be used as a guide. Product specs and design are subject to change at any time.
\end{enumerate}



