%%%%%%%%%%%%
%
% $Autor: Sudeshna $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: SetUp.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Set Up}

\section{Detailed Description of Assembly}

\subsection{Prepare the Board}
\begin{enumerate}
	\item Connect the \textbf{Arduino Nano 33 BLE Sense} to your computer using a \textbf{micro USB cable}.
	\item Open the \textbf{Arduino IDE} and ensure the board is recognized:
	\begin{itemize}
		\item Go to \texttt{Tools} $\to$ \texttt{Board} $\to$ Select \textbf{Arduino Nano 33 BLE Sense}.
		\item Go to \texttt{Tools} $\to$ \texttt{Port} $\to$ Select the correct COM port.
	\end{itemize}
	\item If required, install the board package:
	\begin{itemize}
		\item Open \textbf{Boards Manager} in Arduino IDE.
		\item Search for \texttt{Arduino mbed OS Nano Boards} and install it.
	\end{itemize}
\end{enumerate}

\subsection{Upload the Firmware}
\begin{enumerate}
	\item Install necessary libraries via the \textbf{Arduino Library Manager}:
	\begin{itemize}
		\item \texttt{TensorFlowLite} (for ML model execution)
		\item \texttt{Arduino\_LSM9DS1} (for IMU sensor integration)
	\end{itemize}
	\item Open the firmware source file:
	\begin{itemize}
		\item Navigate to \texttt{src/main.cpp}.
		\item Load the firmware sketch into the Arduino IDE.
	\end{itemize}
	\item Verify the code by clicking the \textbf{Checkmark icon}.
	\item Upload the firmware by clicking the \textbf{Upload (→) icon}.
	\item Open the \textbf{Serial Monitor} (\texttt{Tools} $\to$ \texttt{Serial Monitor}) and set baud rate to \texttt{115200}.
\end{enumerate}

\subsection{Integrate the Sensors and Components}
\begin{itemize}
	\item \textbf{Onboard IMU (LSM9DS1) Setup}
	\begin{itemize}
		\item The \textbf{Inertial Measurement Unit (IMU)} detects motion and gestures.
		\item No additional wiring is needed as it is built into the board.
	\end{itemize}
	\item \textbf{Optional External Components}
	\begin{itemize}
		\item \textbf{RGB LEDs} for visual feedback:
		\begin{itemize}
			\item Connect Red, Green, and Blue (RGB) pins to digital PWM-capable pins on the Arduino.
			\item Use a common ground (GND).
		\end{itemize}
		\item \textbf{Vibration Motor} for haptic feedback:
		\begin{itemize}
			\item Connect the positive terminal to a PWM digital pin.
			\item Use a transistor and a diode for safe operation.
			\item Connect the negative terminal to GND.
		\end{itemize}
	\end{itemize}
\end{itemize}

\subsection{Testing the Gesture Recognition}
\begin{enumerate}
	\item Open the \textbf{Serial Monitor} to observe real-time sensor data.
	\item Run the command:
	\begin{lstlisting}[language=sh]
		edge-impulse-run-impulse
	\end{lstlisting}
	\item Observe classification results and verify correct gesture recognition.
	\item If necessary, retrain or fine-tune the machine learning model.
\end{enumerate}

\subsection{Final Assembly}
\begin{enumerate}
	\item Carefully place the \textbf{Arduino Nano 33 BLE Sense} inside the wand casing.
	\item Ensure the \textbf{USB port remains accessible} for firmware updates and charging.
	\item Securely route any external component wiring inside the casing.
	\item Seal the casing while allowing necessary access points for LEDs or buttons.
	\item Perform a final functionality test to confirm all components work as expected.
\end{enumerate}
